Comparative Analysis of the wav2vec 2.0 Feature Extractor

### 2023-03-09 figures/masked_filters.tex
squeeze space

\begin{figure}[htb]
	% blog post on how to use pgf from matplotlib to latex
	% https://timodenk.com/blog/exporting-matplotlib-plots-to-latex/
	% \usepackage{layouts} and \printinunitsof{cm}\prntlen{\textwidth} show that textwidth is 17cm here.
	\centering
	\input{figures/masked_filters.pgf}
	\vspace{-0.3cm}
	\caption{\gls{WER} [\%] on \devother using the \gls{SC} features, where $N$ filters of the first layer are masked out based on the peak-to-average value of their frequency response.}
	\label{fig:masked_filters}
\end{figure}

>>>>

\begin{figure}[htb]
	% blog post on how to use pgf from matplotlib to latex
	% https://timodenk.com/blog/exporting-matplotlib-plots-to-latex/
	% \usepackage{layouts} and \printinunitsof{cm}\prntlen{\textwidth} show that textwidth is 17cm here.
	\centering
	\input{figures/masked_filters.pgf}
	\vspace{-0.3cm}
	\caption{\gls{WER} [\%] on \devother using the \gls{SC} features, where $N$ out of 150 filters of the first layer are masked in recognition based on the peak-to-average ratio of their frequency response.\vspace{-1cm}}
	\label{fig:masked_filters}
\end{figure}
